Finite Property Convex Elicitation Paper

### 2019-01-30 cvx-fin.tex
Read through of embeddability bounds section and added notes

\begin{proposition}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}
  \item $\Gamma$ embeds a finite elicitable property $\gamma:\simplex \toto \R$.
    \raf{I think we don't need elicitability of $\gamma$ for the TFAE, right?  If so, let's remove it here (just ``finite property'') and add it to the moreover (``, and $\gamma$ is elicitable.'')  The proof that $\trim(\Gamma)$ (with some labels) is elicitable I think is in my notes.}
  \item $\trim(\Gamma)$ is a finite set.
  \item There is a finite set of maximal level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
  \end{enumerate}
  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$.
\end{proposition}
\begin{proof}
  For $1 \implies 2$, since $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R) \} = \{\gamma_r : r \in \R\}$.
  (Note that the second equality follows from the definition of embedding.)
  Clearly, $\trim(\Gamma) \supseteq \{\gamma_r : r \in \R\}$ as we are simply restricting the number of level sets we are indexing over.
  Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
  If $u \in \varphi(\R)$, then clearly we are done.
  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since the level sets composing $\trim$ are unlabeled.
  If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
  If $\Gamma_u$ is maximal, it must be unique up to relabeling (see Lemma~\ref{lem:trim-subsets-not-maximal} in the Appendix)\jessiet{skimmed over this, but follows from the convexity of the scoring rule.  My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}, giving us one of the first two cases or a contradiction of elicitability.
  If $\Gamma_u$ is not maximal, it must be a subset of some maximal level set\jessiet{also in my notes... going to suggest the same footnote/appendix proof- like the other note.}, and therefore not in $\trim(\Gamma)$.
  Thus, we conclude $\trim(\Gamma) \subseteq \{\gamma_r : r \in \R\}$ and since the sets are equal, can conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.

  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is maximal, suppose for now that $\Theta := \trim(\Gamma)$.
  %As $\Gamma$ is nondegenerate, for every $p \in \simplex$, there must be some report $u$ corresponding to the level set such that $p \in \Gamma_u$.
  Because $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only non-maximal level sets are removed in taking $\trim(\Gamma)$.
  If, for some $p\in \simplex$, the level set $\Gamma_u$ corresponding to $p$ was removed, it would be because there is a level set corresponding to $w \in \reals^d$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.

  For $3 \implies 1$, take the set $\R := \{u : \Gamma_u \in\trim(\Gamma)\}$.
  (Take only one such report per level set.)
  The set $\R$ is then finite, and taking $\varphi$ to be the identity, we observe that $\Gamma$ embeds $\gamma: p \mapsto \Gamma(p) \cap \R$.
  We can then see $\gamma$ is elicitable by the loss $L|_{\R}$, where $L$ is the convex surrogate eliciting $\Gamma$.
\end{proof}

% \begin{proof}
% 	We proceed in a cycle to show $1 \implies 2 \implies 3 \implies 1 $.
% 	\begin{enumerate}
% 		\item [$1 \implies 2$]
% 		We know $\strip(\gamma) = \trim(\Gamma)$ (since $\varphi$ is an injection, and there is some intermediate property $\Gamma'$ such that $\Gamma' \preceq \Gamma$ and with a bijection $\phi:\Gamma'(p) \mapsto \gamma(p)$, so $\strip(\Gamma') = \strip(\gamma)$.) 
% 		As $\gamma$ is finite, so is $\strip(\gamma)$ since strip is generated from the (finite) report set.

% 		\item [$2 \implies 3$]
% 		Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional, it is clear that the union of the level sets of $\trim(\Gamma)$ union to $\simplex$ by nondegneracy of $\Gamma$.

% 		\item[$3 \implies 1$]
% 		Construct $\R := \{[u] \in \Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$.
% 		The property $\gamma: p \mapsto \Gamma(p) \cap\R$ is then finite as $\R$ is finite.
% 		Taking $\varphi$ to be the identity, $\Gamma$ embeds this finite $\gamma$.
% 	\end{enumerate} 
% \end{proof}

@@

\raf{Note the relationship to Finocchiaro 2018, and that this is nearly a corollary, as that work almost shows $5\implies 4$, but it needs slightly more assumptions than we need.  Instead, we give a direct proof.}

@@

Recall that a \emph{halfspace-representation (H-rep)} of a closed polyhedral set $S$ in $d$ dimensions is a pair $(V,b)$ with $V \in \reals^{k \times d}$ and $b \in \reals^k$ such that $S = \{ w : Vw \leq b \}$.
We say an H-rep is \emph{tight} if for all $i=1,\dots,k$, there exists $w \in S$ such that $\langle V_i , w \rangle = b_i$.

@@

\begin{corollary}
  If a property is $d$-embeddable, then each of its level sets has a $d$-construction.
  \bo{Is it possible that some uniqueness of the construction is also true?}
\end{corollary}
\begin{proof}
  Suppose the level set is represented as $\Gamma_r = \{p : Bp \geq 0\}$ with $B \in \reals^{k \times n}$ for the minimum $k$ (i.e. the number of facets of the polytope).
  Let $u \in \reals^d$ be its embedding point.
  The convex expected loss is minimized at $u$ if and only if it has the zero vector as a subgradient at $u$, i.e.
    \[ p \in \Gamma_r \qquad \iff \qquad 0 \in \partial \langle L(u), p \rangle . \]
  Subgradient sets satisfy the following two properties: $\partial(f_1 + f_2) = \partial f_1 + \partial f_2$ where the right side is the Minkowski sum of the subgradient sets (i.e. the set of sums of all pairs); and $\partial(\alpha f_1) = \alpha \partial f_1$.
  So
    \[ \partial \langle p , L(u) \rangle = \sum_{y \in \Y} p_y \partial L(u)_y \]
  where the right side is a Minkowski sum of subgradient sets.
  We now consider the halfspaces defining this set.
  Define the $y$th support function as $H_y(v) = \max_{w \in \partial L(u)_y} \langle w, v \rangle$ to obtain that $w \in \partial \langle p, L(u) \rangle$ if and only if, for all unit vectors $v$,
   \[ \langle v, w \rangle \leq \sum_{y \in \Y} p_y H_y(v) . \]
  In particular, the embedding point is optimal for $p$ if and only if this is satisfied for $w=0$.
  So, letting $B_i$ be the $i$th column of $B$, we have
    \[ \Gamma_r = \{p : \sum_y p_y B_y \geq 0\} = \{p : \sum_y p_y H_y(v) \geq 0 ~ (\forall v, \|v\|=1)\} . \]
  \bo{This is the part I'm still not perfectly happy with}
  These sets are equal and full-dimensional (as the property is finite and non-redundant and $B$ is minimal).
  So there exist $k$ unit vectors $v_1,\dots,v_k \in \reals^d$ such that $H_y(v_i) = B_{iy}$.
  Collected as rows of $V$, we obtain that each $(V,B_y)$ is a tight halfspace representation, as it contains $\partial L(u)_y$ and $H_y(v_i) = B_{iy}$, meaning there exists $w \in \partial L(u)_y$ such that $\langle w, v_i \rangle = B_{iy}$.
\end{proof}
This provides the following recipe for both constructing losses and proving lower bounds.
First, take any level set and represent it as $\{p : Bp \geq 0\}$.
Now if $B$ has $k$ columns, search for a collection of $k$ unit vectors in $\reals^d$.
For any candidate $V$ (whose rows are the unit vectors), a computer program can automatically verify whether the representations $\{(V,B_y)\}_{y \in \Y}$ are tight.
In particular, if any $(V,B_y)$ is infeasible (i.e. there does not exist any $w$ satisfying all constraints $\langle v_i, w \rangle \leq B_{iy}$), then $V$ is not a $d$-construction.
If $(V,B_y)$ is feasible but some constraints are redundant, i.e. it is not tight, then again we do not have a $d$-construction.

@@

\section{Considering unlabeled properties}
  Note that $\Gamma$ is elicitable, which means that there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
  There is a set $\D \subseteq \partial_p G$, and we note that there is a bijection $\phi:\D \to \R$ so that the subgradients of $G$ correspond to the property value at the distribution $p$.

@@

\jessie{Lemma 34 below gets rid of the need for this statement.}
\begin{lemma}\label{lem:trim-full-dim}
  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.  
\end{lemma}
\begin{proof}
  Consider an arbitrary level set $\theta$.
  If $\theta$ is not maximal, we want to show that it must be the intersection of some maximal level sets in $\trim(\Gamma)$.\jessiet{Why?  Add more details about why the level set can't span two maximal level sets}
  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.

  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
  It must then span multiple level sets, which contradicts elicitability of $\Gamma$ \jessiet{Does it though?}
\end{proof}

\begin{lemma}\label{lem:trim-subsets-not-maximal}
Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not maximal.
\end{lemma}
\begin{proof}
  If there is a maximal level set $\Gamma_u$ that is a proper subset of $\Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e. $|\partial_p G(p)| > 1$) for every distribution $p \in \Gamma_u$.
  However, closed, convex, maximal level sets have positive Lebesgue measure in $\reals^n$, and thus $G$ can not be differentiable on $\Gamma_u$.
  This contradicts the convexity of $G$, as convex functions are differentiable almost everywhere, which in turn contradicts the elicitability of $\Gamma$.
  Therefore, we conclude that $\Gamma_u$ is not maximal.
\end{proof}

\begin{lemma}\label{lem:finite-nonred-fdls}
Let $\Gamma:\simplex \toto \R'$ be a nonredundant, finite elicitable property.
Each level set $\Gamma_u \in \{\Gamma_u : u \in \R' \}$ is full-dimensional.
\end{lemma}
\begin{proof}
Let us consider 3 cases: first, we cannot observe a level set is a subset of or equal to another by nonredundancy of the property.
Now, if one level set spans the interiors of two different level sets, we will see that this property is not elicitable.
Since we assume $\Gamma$ is elicitable, we know the score $G$ is convex over $\simplex$.

Now, suppose there are two distributions $q,q'$ such that $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ for $u \neq u'$. 
Additionally, if there is a report $w$ such that $\conv(\{q,q'\}) \subseteq \Gamma_w$, we say that the level set $\Gamma_w$ spans the interior of two level sets.

First, consider that if $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ are two nonredundant points in the set $S$ such that $\Gamma_w = \conv(S)$, then there are distributions $p := q + \epsilon(q-q')$ and $p' = q' + \epsilon(q'-q)$ that are both in the interior of their respective level sets and $\Gamma(p) \cap \Gamma(p') = \emptyset$.
By \jessie{Raf and Ian 2018} Lemma 10, then for $\lambda \in (0,1)$, the score $G(\lambda p + (1-\lambda) p') < \lambda G(p) + (1-\lambda) G(p')$.
However, if $q$ and $q'$ share a subgradient, then the score $G$ is flat on $\conv(\{q,q'\})$, which is a subset of $\conv(\{p,p'\})$.
However, this contradicts \jessie{Raf and Ian 2018} Lemma 10, as the score $G$ is flat (and therefore the strict inequality is actually an equality) on $(a,b) \subseteq (0,1)$.

Now, if the level set $\Gamma_w$ is described as the convex hull of distributions $q \not \in \inter{\Gamma_u}$ or $q' \not \in \inter{\Gamma_{u'}}$, such distributions $p$ and $p'$ do not exist in the respective level sets.
\jessie{.... other argument}

Therefore, for the elicitable property $\Gamma$, there cannot be a level set $\Gamma_w$ that spans the interiors of two other level sets.

>>>>

\begin{proposition}\label{prop:embed-trim}
  Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
  The following are equivalent:
  \begin{enumerate}
  \item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
    \raf{I think we don't need elicitability of $\gamma$ for the TFAE, right?  If so, let's remove it here (just ``finite property'') and add it to the moreover (``, and $\gamma$ is elicitable.'')  The proof that $\trim(\Gamma)$ (with some labels) is elicitable I think is in my notes.}\jessie{That sounds good to me, as long as $\Gamma$ is still elicitable.}
  \item $\trim(\Gamma)$ is a finite set.
  \item There is a finite set of maximal level sets $\Theta$ of $\Gamma$ that union to $\simplex$.
  \end{enumerate}
  Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
\end{proposition}
\begin{proof}
  For $1 \implies 2$, since $\Gamma$ embeds the finite property $\gamma$, we show that $\trim(\Gamma) = \{\Gamma_u : u \in \varphi(\R) \} = \{\gamma_r : r \in \R\}$.
  (Note that the second equality follows from the definition of embedding.)
  Clearly, $\trim(\Gamma) \supseteq \{\Gamma_u : u \in \varphi(\R)\}$ as we are simply restricting the number of level sets we are indexing over.
  Now, consider some $\theta \in \trim(\Gamma)$ and the report $u$ so that $\theta = \Gamma_u$.
  If $u \in \varphi(\R)$, then clearly we are done.
  If $u \not\in \varphi(\R)$ but there is some report $w \in \varphi(\R)$ so that $\Gamma_u = \Gamma_w$, then we are again done since the level sets composing $\trim$ are unlabeled.
  If there is no such $w \in \R$, then we claim $\Gamma_u \not \in \trim(\Gamma)$.
  If $\Gamma_u$ is maximal, it must be unique up to relabeling (see Lemma~\ref{lem:trim-subsets-not-maximal} in the Appendix)\jessiet{skimmed over this, but follows from the convexity of the scoring rule.  My thought for the paper is to put that proof in the appendix,and just have a footnote or side note here with a reference to the proof in the appendix.}, giving us one of the first two cases or a contradiction of elicitability.
  If $\Gamma_u$ is not maximal, it must be a subset of some maximal level set by Lemma~\ref{lem:trim-subsets-not-maximal}, and therefore not in $\trim(\Gamma)$.
  Thus, we conclude $\trim(\Gamma) \subseteq \{\gamma_r : r \in \R\}$ and since the sets are equal, can conclude that if $\Gamma$ embeds the finite property $\gamma$, then $\trim(\Gamma)$ is finite.

  For $2 \implies 3$, since each level set $\theta \in \trim(\Gamma)$ is full-dimensional, suppose for now that $\Theta := \trim(\Gamma)$.
  %As $\Gamma$ is nondegenerate, for every $p \in \simplex$, there must be some report $u$ corresponding to the level set such that $p \in \Gamma_u$.
  Since $\Gamma$ is nondegenerate, for all $p \in \simplex$, there is a level set $\theta \in \trim(\Gamma)$ such that $p \in \theta$, since the level sets of elicitable properties are closed and convex, and only non-maximal level sets are removed in taking $\trim(\Gamma)$.
  If, for some $p\in \simplex$, the level set $\Gamma_u$ corresponding to $p$ was removed, it would be because there is a level set corresponding to $w \in \reals^d$ such that $\Gamma_u \subset \Gamma_w$, but then $p \in \Gamma_w$.

  For $3 \implies 1$, take the set $\R := \{u : \Gamma_u \in\trim(\Gamma)\}$.
  (Take only one such report per level set.)
  The set $\R$ is then finite, and taking $\varphi$ to be the identity, we observe that $\Gamma$ embeds $\gamma: p \mapsto \Gamma(p) \cap \R$.
  %We can also see $\gamma = \prop{L|_{\R}}$, where $\Gamma = \prop{L}$.
\end{proof}

@@

\raf{Note the relationship to~\cite{finocchiaro2018convex}, and that this is nearly a corollary, as that work almost shows $5\implies 4$, but it needs slightly more assumptions than we need.  Instead, we give a direct proof.}

@@

Recall that a \emph{halfspace-representation (H-rep)} of a closed polyhedral set $S$ in $d$ dimensions is a pair $(V,b)$ with $V \in \reals^{k \times d}$ and $b \in \reals^k$ such that $S = \{ w : Vw \leq b \}$.
We say an H-rep is \emph{tight} if for all $i=1,\dots,k$, there exists $w \in S$ such that $\langle V_i , w \rangle = b_i$.
\jessie{Imagine two planes in $\reals^3$ (constructing the H-rep) intersect on the line $\ell$ and a third plane only intersects the H-rep on $\ell$, but doesn't make the convex polytope any smaller.  Are we still ok with this being considered tight?  (I think I'm saying if each face is not full-dimensional?)}

@@

\begin{corollary}
  If a property is $d$-embeddable, then each of its level sets has a $d$-construction.
  \bo{Is it possible that some uniqueness of the construction is also true?}\jessie{Up to rotation, scaling, and translation, possible but I wouldn't think so.  ex: Abstain(1/2) on 3 outsomes can be embedded in $\reals^2$ with both an equilateral and isosceles triangle}
\end{corollary}
\begin{proof}
  Suppose the level set is represented as $\Gamma_r = \{p : Bp \geq 0\}$ with $B \in \reals^{k \times n}$ for the minimum $k$ (i.e. the number of facets of the polytope).
  Let $u \in \reals^d$ be its embedding point.
  The convex expected loss is minimized at $u$ if and only if it has the zero vector as a subgradient at $u$, i.e.
    \[ p \in \Gamma_r \qquad \iff \qquad 0 \in \partial \langle L(u), p \rangle . \]
  Subgradient sets satisfy the following two properties: $\partial(f_1 + f_2) = \partial f_1 + \partial f_2$ where the right side is the Minkowski sum of the subgradient sets (i.e. the set of sums of all pairs); and $\partial(\alpha f_1) = \alpha \partial f_1$.
  So
    \[ \partial \langle p , L(u) \rangle = \sum_{y \in \Y} p_y \partial L(u)_y \]
  where the right side is a Minkowski sum of subgradient sets.
  We now consider the halfspaces defining this set.
  Define the $y$th support function as $H_y(v) = \max_{w \in \partial L(u)_y} \langle w, v \rangle$ to obtain that $w \in \partial \langle p, L(u) \rangle$ if and only if, for all unit vectors $v$,
   \[ \langle v, w \rangle \leq \sum_{y \in \Y} p_y H_y(v) . \]
  In particular, the embedding point is optimal for $p$ if and only if this is satisfied for $w=0$.
  So, letting $B_i$ be the $i$th column of $B$, we have
    \[ \Gamma_r = \{p : \sum_y p_y B_y \geq 0\} = \{p : \sum_y p_y H_y(v) \geq 0 ~ (\forall v, \|v\|=1)\} . \]
  \bo{This is the part I'm still not perfectly happy with}
  These sets are equal and full-dimensional (as the property is finite and non-redundant and $B$ is minimal).
  So there exist $k$ unit vectors $v_1,\dots,v_k \in \reals^d$ such that $H_y(v_i) = B_{iy}$.
  Collected as rows of $V$, we obtain that each $(V,B_y)$ is a tight halfspace representation, as it contains $\partial L(u)_y$ and $H_y(v_i) = B_{iy}$, meaning there exists $w \in \partial L(u)_y$ such that $\langle w, v_i \rangle = B_{iy}$.
\end{proof}
This provides the following recipe for both constructing losses and proving lower bounds.
First, take any level set and represent it as $\{p : Bp \geq 0\}$.
Now if $B$ has $k$ columns, search for a collection of $k$ unit vectors in $\reals^d$.
For any candidate $V$ (whose rows are the unit vectors), a computer program can automatically verify whether the representations $\{(V,B_y)\}_{y \in \Y}$ are tight.
In particular, if any $(V,B_y)$ is infeasible (i.e. there does not exist any $w$ satisfying all constraints $\langle v_i, w \rangle \leq B_{iy}$), then $V$ is not a $d$-construction.
If $(V,B_y)$ is feasible but some constraints are redundant, i.e. it is not tight, then again we do not have a $d$-construction.

@@

\section{Considering unlabeled properties}
  Note that $\Gamma$ is elicitable, which means that there is a convex score $G:\simplex \to \reals$ representing the Bayes Risk (i.e. $G(p)$ is the minimal expected loss over all reports at $p$.)
  There is a set $\D \subseteq \partial_p G$ so that there is a bijection $\phi:\D \to \R$.
  Therefore, the subgradients of $G$ correspond to the property value at the distribution $p$.

@@

%\jessie{Lemma \ref{lem:trim-subsets-not-maximal} below gets rid of the need for this statement.}
%\begin{lemma}\label{lem:trim-full-dim}
%  Consider a nondegenerate, elicitable property $\Gamma$ with finitely many level sets.
%  Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional.  
%\end{lemma}
%\begin{proof}
%  Consider an arbitrary level set $\theta$.
%  If $\theta$ is not maximal, we want to show that it must be the intersection of some maximal level sets in $\trim(\Gamma)$.\jessiet{Why?  Add more details about why the level set can't span two maximal level sets}
%  If it is a proper subset of the level sets of which it is the intersection, and so it is not in the $\trim$ as it is in the subtracted set.

%  Now suppose that a level set $\theta$ was not full-dimensional and not a proper subset of any one level set.
%  It must then span multiple level sets, which contradicts elicitability of $\Gamma$ \jessiet{Does it though?}
%\end{proof}

\begin{lemma}\label{lem:trim-subsets-not-maximal}
Let $\Gamma:\simplex \toto \R'$ be an elicitable property.
For any $u,w \in \R'$, if $\Gamma_u \subsetneq \Gamma_w$, then $\Gamma_u$ is not full dimensional.
\end{lemma}
\begin{proof}
  If there is a maximal level set $\Gamma_u$ that is a proper subset of $\Gamma_w$, then the corresponding scoring rule $G$ must not be differentiable (i.e. $|\partial_p G(p)| > 1$) for every distribution $p \in \Gamma_u$.
  However, closed, convex, maximal level sets have positive Lebesgue measure in $\reals^n$, and thus $G$ can not be differentiable on $\Gamma_u$.
  This contradicts the convexity of $G$, as convex functions are differentiable almost everywhere, which in turn contradicts the elicitability of $\Gamma$.
  Therefore, we conclude that $\Gamma_u$ is not maximal.
\end{proof}

\begin{lemma}\label{lem:unique-opt-on-inter}
  Let $\Gamma:\simplex \toto \R'$ be a nonredundant, elicitable property.
  For all $u \in \R'$, if $p \in \inter{\Gamma_u}$, then $\Gamma(p) = \{u\}$.
\end{lemma}
\begin{proof}
\jessiet{Come back and formalize}
  We'll use the relationship between nonredundant properties and subgradients of the expected score $G$.
  Now consider the following convex analysis fact: for any convex function and any two point which share a subgradient, the function is flat between those points.
  In particular, $G$ is flat on $\Gamma_u$, and therefore $G$ must be differentiable on the interior of $\Gamma_u$.
  Therefore, $G$ must only have one subgradient on $\inter{\Gamma_u}$.
\end{proof}

\begin{corollary}
  If $\Gamma:\simplex \toto \R'$ is a nonredundant, finite elicitable property, no level set spans the interior of two other level sets.
  Formally, there is no $w \in \R'$ so that for any $p \in \inter{\Gamma_u}$ and $q \in \inter{\Gamma_v}$, $p,q \in \Gamma_w$ for reports $u,v \in \R'$.
\end{corollary}

%\begin{lemma}\label{lem:finite-nonred-fdls}
%Let $\Gamma:\simplex \toto \R'$ be a nonredundant, finite elicitable property.
%Each level set $\Gamma_u \in \{\Gamma_u : u \in \R' \}$ is full-dimensional.
%\end{lemma}
%\begin{proof}
%Let us consider 3 cases: first, we cannot observe a level set is a subset of or equal to another by nonredundancy of the property.
%Now, if one level set spans the interiors of two different level sets, we will see that this property is not elicitable.
%Since we assume $\Gamma$ is elicitable, we know the score $G$ is convex over $\simplex$.

%Now, suppose there are two distributions $q,q'$ such that $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ for $u \neq u'$. 
%Additionally, if there is a report $w$ such that $\conv(\{q,q'\}) \subseteq \Gamma_w$, we say that the level set $\Gamma_w$ spans the interior of two level sets.

%First, consider that if $q \in \inter{\Gamma_u}$ and $q' \in \inter{\Gamma_{u'}}$ are two nonredundant points in the set $S$ such that $\Gamma_w = \conv(S)$, then there are distributions $p := q + \epsilon(q-q')$ and $p' = q' + \epsilon(q'-q)$ that are both in the interior of their respective level sets and $\Gamma(p) \cap \Gamma(p') = \emptyset$.
%By \jessie{Raf and Ian 2018} Lemma 10, then for $\lambda \in (0,1)$, the score $G(\lambda p + (1-\lambda) p') < \lambda G(p) + (1-\lambda) G(p')$.
%However, if $q$ and $q'$ share a subgradient, then the score $G$ is flat on $\conv(\{q,q'\})$, which is a subset of $\conv(\{p,p'\})$.
%However, this contradicts \jessie{Raf and Ian 2018} Lemma 10, as the score $G$ is flat (and therefore the strict inequality is actually an equality) on $(a,b) \subseteq (0,1)$.

%Now, if the level set $\Gamma_w$ is described as the convex hull of distributions $q \not \in \inter{\Gamma_u}$ or $q' \not \in \inter{\Gamma_{u'}}$, such distributions $p$ and $p'$ do not exist in the respective level sets.
%\jessie{.... other argument}

%Therefore, for the elicitable property $\Gamma$, there cannot be a level set $\Gamma_w$ that spans the interiors of two other level set.s

%\end{proof}
